VIPE: Virtualized Intermittently-Powered Executor

### 2017-07-24 paper/iposDataProtection.tex
change VIPOS to \sys

\subsection{VIPOS: Data/Memory Protection Methods}

@@

VIPOS data consistency preservation methods are designed with goal of minimal interaction between the CPU and FRAM to reduce energy consumption (see Section~\ref{sec:prelResults}). These data/memory protection methods enables VIPOS to tolerate arbitrary number of power failures.

@@

		We implement a reference implementation of VIPOS that uses virtualized Operational buffer to protect the data against power failure. 
		\paragraph{Virtual Buffer}
			We realized the virtaulzed buffer as a volatile hashed table of linked lists. The hashing technique was chosen to reduce the buffer searching time and the linked lists are used to prevent data loss when there is a conflict between multiple variables---If two variables have the same hash value they will occupy the same cell, however, with linked list a new node will be created for each variable to resolve the conflict and protect the data. The hashing function is based on the observation that the virtual addresses of the memory cells have approximately a flat distribution over the memory addressing space and the fact that each entry, of the virtual table, has the address and the value of a variable. As such, by using the least significant bits as an index to access the virtual buffer the hash function distributes its inputs uniformly in the virtual buffer. Accordingly, the linked lists search time, on average, is reduced.

@@

		\paragraph{Persistent Buffer}
			The persistent buffer is implemented as static array of tuples, where each tuple holds  the address and the value of a variable. This data structure is very suitable for the second phase commit where each element has to be committed to its finial location. However, the complexity of committing this buffer is of size $O(N)$, where $N$ equals the length of the buffer. Therefore, the size of the buffer can have dramatic effect on the performance of VIPOS---On one hand, if the size of the buffer is small the buffer overflow problem will be very serious. On the other hand, if the size of the buffer is large VIPOS will experience a significant performance degradation. However, by observing the type of the information that this buffer holds, namely memory addresses, we can, on average, reduce the complexity of committing this buffer by defining the \emph{effective size} of the buffer to be the size of the buffer up to the first cell that holds an invalid memory address. Moreover, since this buffer is in FRAM which is much bigger than SRAM its size can be relatively big.

@@

		% \begin{figure}[t]
		% 	\centering
		% 	\includegraphics[width=\columnwidth]{figures/virtual_buffer_size.eps}
		% 	\caption{VIPOS based on virtualized Operational Buffer. It runs the decompression application with different buffer configurarions. EPB: Enhanced Persistent Buffer. NR: no read operation from the buffer. NRW: not read or write operations from the buffer.}
		% 	\label{fig:virtOperationalBuf}
		% \end{figure}

		% 	To analyze the performance of VIPOS versus the sizes of the virtual buffer and the persistent buffer we setup the following experiment. We let IPOS to run the decompression application---until the data decompression is completely finished---and we capture the execution time using a logic analyzer~\cite{xxx}. The results presented in Fig.~\ref{fig:virtOperationalBuf} show the VIPOS has its best performance when the virtual buffer size is 16, where the execution time was $\approx$196 ms.

		% 	All the experiments were done with a persistent buffer of size 100. However, the bar labeled with "EPB/16" in  Fig.~\ref{fig:virtOperationalBuf} shows the effect of the enhanced commit process that uses the buffer effective size instead of the buffer maximum size. We see that the execution time is reduced to $\approx$80 ms. Furthermore, we quantized the overhead of the read operations from the buffer, by eliminating this operation, and the bar labeled with "NR" shows that it cost  $\approx$10 ms. Moreover, the overhead of the read and write operations is $\approx$34 ms as compared to VIPOS best performance, see the bar labeled with "NRW" in Fig.~\ref{fig:virtOperationalBuf}.

>>>>

\subsection{\sys: Data/Memory Protection Methods}

@@

\sys data consistency preservation methods are designed with goal of minimal interaction between the CPU and FRAM to reduce energy consumption (see Section~\ref{sec:prelResults}). These data/memory protection methods enables \sys to tolerate arbitrary number of power failures.

@@

		We implement a reference implementation of \sys that uses virtualized Operational buffer to protect the data against power failure. 
		\paragraph{Virtual Buffer}
			We realized the virtaulzed buffer as a volatile hashed table of linked lists. The hashing technique was chosen to reduce the buffer searching time and the linked lists are used to prevent data loss when there is a conflict between multiple variables---If two variables have the same hash value they will occupy the same cell, however, with linked list a new node will be created for each variable to resolve the conflict and protect the data. The hashing function is based on the observation that the virtual addresses of the memory cells have approximately a flat distribution over the memory addressing space and the fact that each entry, of the virtual table, has the address and the value of a variable. As such, by using the least significant bits as an index to access the virtual buffer the hash function distributes its inputs uniformly in the virtual buffer. Accordingly, the linked lists search time, on average, is reduced.

@@

		\paragraph{Persistent Buffer}
			The persistent buffer is implemented as static array of tuples, where each tuple holds  the address and the value of a variable. This data structure is very suitable for the second phase commit where each element has to be committed to its finial location. However, the complexity of committing this buffer is of size $O(N)$, where $N$ equals the length of the buffer. Therefore, the size of the buffer can have dramatic effect on the performance of \sys---On one hand, if the size of the buffer is small the buffer overflow problem will be very serious. On the other hand, if the size of the buffer is large \sys will experience a significant performance degradation. However, by observing the type of the information that this buffer holds, namely memory addresses, we can, on average, reduce the complexity of committing this buffer by defining the \emph{effective size} of the buffer to be the size of the buffer up to the first cell that holds an invalid memory address. Moreover, since this buffer is in FRAM which is much bigger than SRAM its size can be relatively big.

@@

		% \begin{figure}[t]
		% 	\centering
		% 	\includegraphics[width=\columnwidth]{figures/virtual_buffer_size.eps}
		% 	\caption{\sys based on virtualized Operational Buffer. It runs the decompression application with different buffer configurarions. EPB: Enhanced Persistent Buffer. NR: no read operation from the buffer. NRW: not read or write operations from the buffer.}
		% 	\label{fig:virtOperationalBuf}
		% \end{figure}

		% 	To analyze the performance of \sys versus the sizes of the virtual buffer and the persistent buffer we setup the following experiment. We let IPOS to run the decompression application---until the data decompression is completely finished---and we capture the execution time using a logic analyzer~\cite{xxx}. The results presented in Fig.~\ref{fig:virtOperationalBuf} show the \sys has its best performance when the virtual buffer size is 16, where the execution time was $\approx$196 ms.

		% 	All the experiments were done with a persistent buffer of size 100. However, the bar labeled with "EPB/16" in  Fig.~\ref{fig:virtOperationalBuf} shows the effect of the enhanced commit process that uses the buffer effective size instead of the buffer maximum size. We see that the execution time is reduced to $\approx$80 ms. Furthermore, we quantized the overhead of the read operations from the buffer, by eliminating this operation, and the bar labeled with "NR" shows that it cost  $\approx$10 ms. Moreover, the overhead of the read and write operations is $\approx$34 ms as compared to \sys best performance, see the bar labeled with "NRW" in Fig.~\ref{fig:virtOperationalBuf}.
